% ============================================================
%  DecodedSound — Full PRD + Engineering Spec v3.3
%  Single source of truth | Overleaf | pdflatex x2
% ============================================================
\documentclass[12pt, a4paper]{article}

\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.8cm, right=2.8cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{colortbl}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{tcolorbox}
\usepackage{listings}
\tcbuselibrary{skins, breakable}

% ── Colours ─────────────────────────────────────────────────
\definecolor{brandpurple}{HTML}{6B35D9}
\definecolor{brandlight}{HTML}{EDE5FF}
\definecolor{accent}{HTML}{FF6B35}
\definecolor{darkbg}{HTML}{1A1A2E}
\definecolor{lightbg}{HTML}{F8F7FF}
\definecolor{midgray}{HTML}{6B7280}
\definecolor{rowalt}{HTML}{F3F0FF}
\definecolor{successgreen}{HTML}{10B981}
\definecolor{codebg}{HTML}{F1F0FF}
\definecolor{warnyellow}{HTML}{F59E0B}
\definecolor{codered}{HTML}{EF4444}

% ── Hyperref ────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  linkcolor=brandpurple,
  urlcolor=brandpurple,
  pdftitle={DecodedSound — Full PRD + Engineering Spec v3.2},
}

% ── Section Formatting ──────────────────────────────────────
\titleformat{\section}
  {\Large\bfseries\color{darkbg}}
  {\color{brandpurple}\thesection.}{0.6em}{}
  [\vspace{-0.4em}\textcolor{brandpurple}{\rule{\linewidth}{2pt}}]

\titleformat{\subsection}
  {\normalsize\bfseries\color{brandpurple}}
  {\thesubsection}{0.6em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{darkbg}}
  {}{0em}{}

\titlespacing*{\section}{0pt}{2em}{0.8em}
\titlespacing*{\subsection}{0pt}{1.2em}{0.4em}
\titlespacing*{\subsubsection}{0pt}{0.8em}{0.3em}

% ── Header / Footer ─────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\color{midgray}\textbf{DecodedSound} — PRD + Engineering Spec v3.3}
\fancyhead[R]{\small\color{midgray}March 2026}
\fancyfoot[C]{\small\color{midgray}\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{%
  \color{brandpurple}\leaders\hrule height\headrulewidth\hfill}}

% ── Box Styles ──────────────────────────────────────────────
\tcbset{
  prdbox/.style={
    enhanced, breakable,
    colback=lightbg, colframe=brandpurple,
    leftrule=4pt, toprule=0.5pt, bottomrule=0.5pt, rightrule=0.5pt,
    left=10pt, right=8pt, top=8pt, bottom=8pt,
    fonttitle=\bfseries\color{brandpurple},
  },
  calloutbox/.style={
    enhanced, breakable,
    colback=brandlight, colframe=brandpurple,
    arc=4pt, boxrule=1pt,
    left=12pt, right=12pt, top=10pt, bottom=10pt,
    fonttitle=\bfseries\color{brandpurple},
  },
  accentbox/.style={
    enhanced,
    colback=accent!10, colframe=accent,
    leftrule=4pt, toprule=0.5pt, bottomrule=0.5pt, rightrule=0.5pt,
    left=10pt, right=8pt, top=8pt, bottom=8pt,
  },
  darkbox/.style={
    enhanced,
    colback=darkbg, colframe=darkbg,
    arc=4pt, boxrule=0pt,
    left=14pt, right=14pt, top=12pt, bottom=12pt,
  },
  storybox/.style={
    enhanced, breakable,
    colback=successgreen!7, colframe=successgreen,
    leftrule=4pt, toprule=0.5pt, bottomrule=0.5pt, rightrule=0.5pt,
    left=10pt, right=8pt, top=6pt, bottom=6pt,
    fonttitle=\bfseries\color{successgreen!70!black},
  },
  codebox/.style={
    enhanced, breakable,
    colback=codebg, colframe=brandpurple!30,
    arc=3pt, boxrule=0.5pt,
    left=10pt, right=8pt, top=6pt, bottom=6pt,
    fontupper=\small\ttfamily\color{darkbg},
  },
  warnbox/.style={
    enhanced,
    colback=warnyellow!10, colframe=warnyellow,
    leftrule=4pt, toprule=0.5pt, bottomrule=0.5pt, rightrule=0.5pt,
    left=10pt, right=8pt, top=6pt, bottom=6pt,
  },
  enginebox/.style={
    enhanced, breakable,
    colback=darkbg!5, colframe=darkbg,
    leftrule=4pt, toprule=0.5pt, bottomrule=0.5pt, rightrule=0.5pt,
    left=10pt, right=8pt, top=8pt, bottom=8pt,
    fonttitle=\bfseries\color{darkbg},
  },
}

% ── Code Listings ───────────────────────────────────────────
\lstset{
  basicstyle=\small\ttfamily\color{darkbg},
  backgroundcolor=\color{codebg},
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  frame=none,
  aboveskip=0pt, belowskip=0pt,
}

% ── Table Columns ───────────────────────────────────────────
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

% ── Lists ───────────────────────────────────────────────────
\setlist[itemize]{
  label=\textcolor{brandpurple}{\textbullet},
  leftmargin=1.4em, itemsep=0.3em, topsep=0.4em,
}
\setlist[enumerate]{
  label=\textcolor{brandpurple}{\arabic*.},
  leftmargin=1.4em, itemsep=0.3em, topsep=0.4em,
}

% ============================================================
\begin{document}
% ============================================================

% ── Title Page ──────────────────────────────────────────────
\begin{titlepage}
  \pagecolor{darkbg}\color{white}
  \vspace*{2cm}
  \begin{center}
    {\fontsize{46}{54}\selectfont\bfseries DecodedSound}\\[0.5em]
    {\Large\color{brandlight} SDK / Esdeekid Music Translator}\\[1em]
    \textcolor{brandpurple}{\rule{10cm}{1.5pt}}\\[1em]
    {\large Full PRD + Engineering Spec}\\[0.3em]
    {\normalsize\color{midgray}
      Version 3.3 — Single Source of Truth\quad|\quad March 2026}\\[2cm]
    \begin{tcolorbox}[calloutbox,
        colback=darkbg!60, colframe=brandpurple, width=12cm]
      \centering\color{white}\itshape
      ``Making the culture accessible to the world.''
    \end{tcolorbox}
    \vfill
    {\small\color{midgray}
      \textbf{Genre:} SDK / Esdeekid only (v1.0)\\[0.3em]
      \textbf{Stack:} Next.js 14 · TypeScript · Prisma · Postgres · Vercel\\[0.3em]
      \textbf{AI:} Groq LLaMA 3.3 70B (translation + detection) · Groq Whisper (transcription)\\[0.3em]
      \textbf{Access:} Fully open — no account required at launch\\[0.3em]
      \textbf{Team:} 2 (Founder + AI)\\[0.3em]
      \textbf{Status:} \textcolor{successgreen}{\textbullet}\enspace
        Phase 1 MVP Complete — Pre-Deploy
    }
  \end{center}
\end{titlepage}

\pagecolor{white}\color{darkbg}
\newpage
\tableofcontents
\newpage

% ============================================================
\section{What We're Building \& Why}
% ============================================================

\begin{tcolorbox}[calloutbox, title={The One-Line Pitch}]
  DecodedSound is an AI-powered web platform that translates SDK (esdeekid)
  music into plain, accessible English — giving anyone in the world the tools
  to understand and connect with one of the most culturally rich street music
  genres to come out of South Africa.
\end{tcolorbox}

\vspace{0.6em}

SDK music is not just slang. It is a coded cultural language built on phonetic
wordplay, Cape Flats dialect, Afrikaans and Xhosa borrowings, double meanings,
and hyper-local references that no outsider can decode without help. No tool
exists that does this well. We're building it.

DecodedSound takes audio files, streaming links, or typed lyrics and returns
four things: a plain English translation, a line-by-line annotated breakdown,
a slang dictionary, and a cultural context narrative.

\textbf{Genre scope is SDK / esdeekid only for v1.0.} We do one thing
exceptionally well before expanding. Amapiano, Gqom, Kwaito are roadmapped
for v2.0 only.

\subsection*{Document Metadata}
\renewcommand{\arraystretch}{1.4}
\begin{center}
\begin{tabular}{L{5cm} L{8.5cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Field}} &
  \textcolor{white}{\textbf{Value}} \\
  \rowcolor{rowalt} Product Name      & DecodedSound \\
  Document Version                    & 3.3 — Full PRD + Engineering Spec \\
  \rowcolor{rowalt} Date              & March 2026 \\
  Status                              & \textcolor{successgreen}{\textbf{Phase 1 MVP Complete}} \\
  \rowcolor{rowalt} Genre Scope v1.0  & SDK / Esdeekid only \\
  Genre Scope v2.0                    & + Amapiano, Gqom, Kwaito \\
  \rowcolor{rowalt} Access Model      & Fully open, no account at launch \\
  Platform v1.0                       & Web browser \\
  \rowcolor{rowalt} Platform v2.0     & + Mobile (React Native) \\
  UI Language                         & English (v1.0) \\
  \rowcolor{rowalt} Team              & 2 (Founder + AI) \\
  Monetization                        & TBD — decided before v1.5 \\
\end{tabular}
\end{center}

% ============================================================
\section{Design Principles}
% ============================================================

These are not suggestions. Every decision in the product and in the code must
hold up against these:

\begin{tcolorbox}[prdbox]
\begin{itemize}
  \item \textbf{Cultural respect first} — we translate, we never police or
        sanitise. The goal is understanding, not judgment.
  \item \textbf{Accuracy over speed} — unknown terms are flagged, never
        guessed. Confidence is surfaced to the user.
  \item \textbf{Zero friction at entry} — no account, no signup wall, no
        paywall at launch. Land and translate immediately.
  \item \textbf{SDK focus, no exceptions in v1.0} — one genre done properly
        beats five genres done badly.
  \item \textbf{Build lean} — no service, library, or abstraction gets added
        unless it solves a real problem we have right now.
  \item \textbf{One source of truth} — this document. If it's not in here,
        it doesn't exist yet.
\end{itemize}
\end{tcolorbox}

% ============================================================
\section{Target Users}
% ============================================================

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{3cm} L{4cm} L{6.5cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Persona}} &
  \textcolor{white}{\textbf{Who}} &
  \textcolor{white}{\textbf{Core Need}} \\
  \rowcolor{rowalt}
  The Curious Fan & Loves the music, misses meaning &
  Understand lyrics; connect with the art \\
  The Parent & Teen's parent hearing SDK at home &
  Know what their kid listens to, without judgment \\
  \rowcolor{rowalt}
  The International Listener & Non-SA audience via streaming &
  Context and vocab to appreciate the music \\
  The Journalist & Media covering SA culture &
  Accurate, citable cultural translations \\
  \rowcolor{rowalt}
  The Artist & Emerging SDK artists &
  See how their work lands with an outside audience \\
\end{tabular}
\end{center}

% ============================================================
\section{Core Features}
% ============================================================

\subsection{Input Methods}

\begin{itemize}
  \item \textbf{Typed Lyrics} — paste raw lyrics, hit translate. No upload,
        no processing delay. Fastest path.
  \item \textbf{Audio Upload} — MP3, WAV, M4A up to 50\,MB. Whisper
        transcribes to text, user can edit before translating.
  \item \textbf{YouTube Link} \textemdash{} paste a URL. System always extracts audio
        via yt-dlp and transcribes with Groq Whisper (YouTube auto-captions are
        skipped because YouTube auto-translates Afrikaans to broken English).
        User reviews and edits transcription before translating.
\end{itemize}

\subsection{4-Panel Translation Output}

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{3.5cm} L{10cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Panel}} &
  \textcolor{white}{\textbf{What It Shows}} \\
  \rowcolor{rowalt}
  Plain Translation &
  Full song rewritten in natural, standard English. No jargon. Reads like a translated poem. \\
  Line-by-Line &
  Original line alongside English translation. Slang terms highlighted; tap/hover for KB definition. \\
  \rowcolor{rowalt}
  Slang Dictionary &
  Auto-extracted glossary: term, definition, origin note, example, confidence level. \\
  Cultural Context &
  2--4 paragraph AI-written narrative: who's speaking, to whom, about what, and why it matters culturally. \\
\end{tabular}
\end{center}

\subsection{Slang Knowledge Base (KB)}

The KB is the core differentiator. It is a growing dictionary of SDK-specific
terms that powers all translation outputs and gets smarter over time.

\begin{tcolorbox}[prdbox, title={KB Strategy: AI-First, Community-Validated}]
\begin{itemize}
  \item \textbf{Phase 1 \textemdash{} AI Seeding:} Every submitted song runs through
        Groq LLaMA 3.3 70B which extracts unknown terms and generates provisional
        definitions. These are stored as candidates.
  \item \textbf{Phase 2 — Moderation:} We (the team) review candidates
        in an internal admin queue and approve, edit, or reject them.
        Approved entries enter the live KB.
  \item \textbf{Phase 3 — Community:} Once we have users, community members
        can flag wrong entries and submit new ones. All go through moderation.
  \item \textbf{Ongoing:} Every new song adds new candidates. The KB never
        stops growing.
\end{itemize}
\end{tcolorbox}

\subsection{Public Song Library}

Searchable library of already-translated songs. Browse by artist or recency.
Each entry shows all 4 panels and a community rating. No account needed to
browse or view.

\subsection{Sharing}

Every translated song gets a unique URL (\texttt{/song/[slug]}). Slugs follow
the format \texttt{\{artist\}-\{title\}-\{nanoid(6)\}} for SEO-friendly sharing.
Share button copies to clipboard. Shared pages are fully public.

% ============================================================
\section{User Stories}
% ============================================================

Format: \textit{As a [persona], I want to [action], so that [outcome].}
Acceptance criteria define done.

\subsection{Typed Lyrics Input}

\begin{tcolorbox}[storybox, title={US-01 — Paste and Translate}]
  \textbf{As a} fan, \textbf{I want to} paste lyrics and hit translate,
  \textbf{so that} I get a full breakdown instantly.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Accepts 1--500 lines of text.
    \item Translate button disabled until at least 1 non-empty line present.
    \item All 4 panels populated within 10 seconds for lyrics under 50 lines.
    \item No account or login required at any point.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-02 — Clear and Re-translate}]
  \textbf{As a} user, \textbf{I want to} clear input and paste new lyrics,
  \textbf{so that} I can translate multiple songs in one session.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Clear button resets input and all 4 output panels.
    \item No page reload required.
  \end{itemize}
\end{tcolorbox}

\subsection{Audio Upload}

\begin{tcolorbox}[storybox, title={US-03 — Upload Audio File}]
  \textbf{As a} fan, \textbf{I want to} upload an audio file,
  \textbf{so that} I don't have to type anything.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Accepts MP3, WAV, M4A only. Other formats rejected with clear message.
    \item Files over 50\,MB rejected before upload begins.
    \item Progress bar shown during upload.
    \item Transcribed lyrics displayed in an editable area before translation.
    \item User can fix transcription errors then hit translate.
    \item All 4 panels populated on success.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-04 — Edit Transcription Before Translating}]
  \textbf{As a} user, \textbf{I want to} fix auto-transcribed lyrics,
  \textbf{so that} transcription errors don't break the translation.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Transcribed text shown in editable textarea.
    \item ``Looks good, translate'' button proceeds.
    \item Edits reflected in the final output.
  \end{itemize}
\end{tcolorbox}

\subsection{Streaming Link}

\begin{tcolorbox}[storybox, title={US-05 — Translate via YouTube Link}]
  \textbf{As a} user, \textbf{I want to} paste a YouTube URL and get a
  translation, \textbf{so that} I don't need to download anything.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Accepts \texttt{youtube.com/watch?v=} and \texttt{youtu.be/} formats.
    \item Always extracts audio via yt-dlp and transcribes with Groq Whisper
          (YouTube auto-captions are skipped because YouTube auto-translates
          Afrikaans to broken English).
    \item User reviews and edits transcription before translating.
    \item If song already in library by URL match, cached result served.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-06 — Reject Non-SDK Content}]
  \textbf{As a} user submitting a non-SDK song, \textbf{I want to} be
  clearly told the scope, \textbf{so that} I'm not confused by a bad result.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item High-confidence non-SDK ($>$0.85) shows a friendly genre warning,
          not an error. User can override and proceed anyway.
    \item Low-confidence detection proceeds with a disclaimer banner.
  \end{itemize}
\end{tcolorbox}

\subsection{Translation Output}

\begin{tcolorbox}[storybox, title={US-07 — View Plain Translation}]
  \textbf{As a} parent, \textbf{I want to} read the song in plain English,
  \textbf{so that} I understand it with zero prior knowledge.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Full song in standard English prose, no jargon.
    \item Reads naturally — not word-for-word literal.
    \item Default panel shown after translation completes.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-08 — View Line-by-Line Breakdown}]
  \textbf{As a} fan, \textbf{I want to} see each line beside its translation,
  \textbf{so that} I learn which words mean what.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Original left / top, translation right / bottom. Side-by-side desktop,
          stacked mobile.
    \item Slang terms highlighted in brand purple.
    \item Tap/hover shows inline tooltip with KB definition.
    \item Unknown terms show: ``Not in our dictionary yet — help us define it!''
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-09 — View Slang Dictionary}]
  \textbf{As a} user, \textbf{I want to} see a glossary of all slang,
  \textbf{so that} I learn the vocab for future songs.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item All flagged terms listed alphabetically.
    \item Each entry: term, definition, origin note, example, confidence badge.
    \item Unverified terms visually distinguished.
    \item Clicking a term highlights it in the line-by-line panel.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-10 — View Cultural Context}]
  \textbf{As a} journalist, \textbf{I want to} read a cultural narrative,
  \textbf{so that} I understand the song's story and significance.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item 2--4 paragraph narrative covering who, what, to whom, and why.
    \item Written in accessible, engaging prose.
    \item Labelled: ``AI-generated — community review pending.''
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-11 — Switch Output Panels}]
  \textbf{As a} user, \textbf{I want to} switch between the 4 panels,
  \textbf{so that} I explore at my own pace.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item 4 tabs: Translation, Line by Line, Slang Dictionary, Cultural Context.
    \item Switching is instant — no reload.
    \item Desktop toggle: ``Show all panels'' displays 2×2 grid.
  \end{itemize}
\end{tcolorbox}

\subsection{Knowledge Base \& Community}

\begin{tcolorbox}[storybox, title={US-12 — Flag a Wrong Definition}]
  \textbf{As a} native speaker, \textbf{I want to} flag a bad KB entry,
  \textbf{so that} it gets corrected.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Flag icon on every KB term. No account to flag.
    \item Form: ``What's wrong?'' with text input.
    \item 3+ unresolved flags auto-downgrade entry to Unverified.
    \item Flags appear in admin moderation queue.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-13 — Submit a Missing Definition}]
  \textbf{As a} community member, \textbf{I want to} add a missing term,
  \textbf{so that} the KB grows.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Contribute form: Term, Definition, Origin note, Example sentence.
    \item Stored as KBCandidate — not live until approved by us.
    \item Confirmation: ``Submitted! We'll review it.''
  \end{itemize}
\end{tcolorbox}

\subsection{Library \& Social}

\begin{tcolorbox}[storybox, title={US-14 — Browse Song Library}]
  \textbf{As a} user, \textbf{I want to} browse translated songs,
  \textbf{so that} I can explore without submitting anything.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Song cards: title, artist, date, avg rating.
    \item Default sort: most recently translated. Filter by artist text search.
    \item No account required to browse.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-15 — Rate a Translation}]
  \textbf{As a} user, \textbf{I want to} rate accuracy,
  \textbf{so that} the best translations surface.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item 1--5 star widget. No account needed (session-based dedup).
    \item Avg rating and count displayed.
    \item Songs below 3 stars flagged in admin queue.
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-16 — Share a Translation}]
  \textbf{As a} user, \textbf{I want to} share a translation link,
  \textbf{so that} others can view it without submitting the song.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Every song gets a unique URL: \texttt{/song/[slug]}.
    \item Slug format: \texttt{\{artist\}-\{title\}-\{nanoid(6)\}}.
    \item Shared pages publicly accessible, no account needed.
  \end{itemize}
\end{tcolorbox}

% ============================================================
\section{Error States}
% ============================================================

No raw error codes ever shown to users. Every error is human and helpful.

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{3.8cm} L{5cm} L{4.8cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Scenario}} &
  \textcolor{white}{\textbf{User Message}} &
  \textcolor{white}{\textbf{System Behaviour}} \\
  \rowcolor{rowalt}
  File too large ($>$50\,MB) &
  ``File is too big (max 50\,MB). Trim the audio or paste lyrics instead.'' &
  Reject before upload. \\
  Bad file format &
  ``We only support MP3, WAV, and M4A.'' &
  Reject at file picker. \\
  \rowcolor{rowalt}
  Whisper fails &
  ``Couldn't transcribe this. Try a cleaner recording or paste lyrics manually.'' &
  Log error; offer lyrics fallback. \\
  Geo-blocked link &
  ``Can't access that link in your region. Paste the lyrics instead.'' &
  Offer lyrics fallback. \\
  \rowcolor{rowalt}
  Invalid / dead URL &
  ``That link doesn't work. Check the URL and try again.'' &
  Validate before processing. \\
  Translation timeout &
  ``Taking longer than expected. Try again in a moment.'' &
  Auto-retry once; message on 2nd fail. \\
  \rowcolor{rowalt}
  Non-SDK detected &
  ``Doesn't look like SDK music — we specialise in SDK for now. Try anyway?'' &
  Warning + override button. \\
  Empty lyrics &
  ``Paste some lyrics first!'' &
  Disable button; inline hint. \\
  \rowcolor{rowalt}
  Zero KB matches &
  ``New territory for us — translation provided but dictionary is empty. Help us build it!'' &
  Proceed; show contribute CTA. \\
  Offline &
  ``You're offline. Check your connection.'' &
  Detect offline; pause processing. \\
\end{tabular}
\end{center}

% ============================================================
\section{Data Models}
% ============================================================

\begin{tcolorbox}[warnbox]
  These are the Prisma schema definitions we build from directly.
  Field names here are the field names in the code.
\end{tcolorbox}

\subsection{Song}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model Song {
  id           String        @id @default(cuid())
  title        String        @default("Untitled")
  artist       String        @default("")
  rawLyrics    String        @db.Text
  slug         String        @unique
  inputType    InputType     @default(TYPED)
  sourceUrl    String?
  isPublic     Boolean       @default(true)
  createdAt    DateTime      @default(now())
  updatedAt    DateTime      @updatedAt
  translations Translation[]
  jobs         Job[]
  ratings      Rating[]
}

enum InputType { TYPED  AUDIO  YOUTUBE }
\end{lstlisting}
\end{tcolorbox}

\subsection{Translation}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model Translation {
  id                String   @id @default(cuid())
  songId            String
  song              Song     @relation(fields: [songId], references: [id],
                               onDelete: Cascade)
  plainTranslation  String   @db.Text
  lineByLine        Json
  // [{ original: string, translation: string, flaggedTerms: string[] }]
  culturalContext   String   @db.Text
  unknownTerms      Json     @default("[]")
  // [{ term: string, provisionalDefinition: string, confidence: number }]
  genreConfidence   Float    @default(0)
  overallConfidence Float    @default(0)
  aiModelVersion    String   @default("llama-3.3-70b-versatile")
  processingTimeMs  Int      @default(0)
  createdAt         DateTime @default(now())
}
\end{lstlisting}
\end{tcolorbox}

\subsection{Job (Async Processing Queue)}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model Job {
  id        String    @id @default(cuid())
  type      String    @default("TRANSLATE")
  status    JobStatus @default(PENDING)
  payload   Json?
  songId    String?
  song      Song?     @relation(fields: [songId], references: [id])
  errorMsg  String?
  attempts  Int       @default(0)
  createdAt DateTime  @default(now())
  updatedAt DateTime  @updatedAt
}

enum JobStatus { PENDING  PROCESSING  COMPLETE  FAILED }
\end{lstlisting}
\end{tcolorbox}

\subsection{KBEntry}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model KBEntry {
  id         String        @id @default(cuid())
  term       String        @unique
  definition String        @db.Text
  origin     String?
  example    String?       @db.Text
  confidence Float         @default(0.5)
  isApproved Boolean       @default(false)
  createdAt  DateTime      @default(now())
  updatedAt  DateTime      @updatedAt
  flags      Flag[]
  candidates KBCandidate[]
}
\end{lstlisting}
\end{tcolorbox}

\subsection{KBCandidate}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model KBCandidate {
  id            String   @id @default(cuid())
  term          String
  definition    String   @db.Text
  confidence    Float    @default(0.5)
  kbEntryId     String?
  kbEntry       KBEntry? @relation(fields: [kbEntryId], references: [id])
  translationId String?
  createdAt     DateTime @default(now())
}
\end{lstlisting}
\end{tcolorbox}

\subsection{Contribution}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model Contribution {
  id         String   @id @default(cuid())
  term       String
  definition String   @db.Text
  example    String?
  ip         String
  status     String   @default("PENDING")
  createdAt  DateTime @default(now())
}
\end{lstlisting}
\end{tcolorbox}

\subsection{Rating}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model Rating {
  id        String   @id @default(cuid())
  songId    String
  song      Song     @relation(fields: [songId], references: [id])
  stars     Int      // 1-5
  ip        String
  createdAt DateTime @default(now())

  @@unique([songId, ip]) // one rating per IP per song (upsert on re-rate)
}
\end{lstlisting}
\end{tcolorbox}

\subsection{Flag}
\begin{tcolorbox}[codebox]
\begin{lstlisting}
model Flag {
  id        String   @id @default(cuid())
  kbEntryId String
  kbEntry   KBEntry  @relation(fields: [kbEntryId], references: [id])
  reason    String   @db.Text
  ip        String
  createdAt DateTime @default(now())
}
// 3+ flags auto-downgrade entry: isApproved = false
\end{lstlisting}
\end{tcolorbox}

% ============================================================
\section{API Routes}
% ============================================================

All routes live under \texttt{/app/api/} in the Next.js App Router.
All responses are JSON. Errors follow:
\texttt{\{"error": string\}}.

\subsection{Translation \& Input}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
POST   /api/translate
       Body:    { title?, artist?, lyrics: string }
       Returns: { slug: string }
       // Synchronous. Runs genre detection + KB inject + Groq LLaMA
       // translation. Creates Song + Translation. Redirects to /song/[slug].
       // Rejects if lyrics < 20 chars.

POST   /api/audio
       Body:    multipart/form-data { file: File }
       Returns: { text: string }
       // Groq Whisper transcription (language hint: 'af').
       // Accepts MP3, WAV, M4A, WEBM. Returns transcribed text.
       // User reviews/edits then calls /api/translate.

POST   /api/youtube
       Body:    { url: string }
       Returns: { text: string, title?: string }
       // yt-dlp downloads .webm -> Groq Whisper transcription.
       // Always skips YouTube captions (auto-translate breaks SDK).
       // Validates youtube.com and youtu.be URLs only.
\end{lstlisting}
\end{tcolorbox}

\subsection{Songs}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
GET    /api/songs
       Query:   ?q=string&page=1 (20 per page)
       Returns: { songs: Song[], total, page, totalPages }
       // Public library. Case-insensitive search on title + artist.

GET    /api/songs/[slug]
       Returns: Song with latest translation + avg rating
       // 404 if slug not found.
\end{lstlisting}
\end{tcolorbox}

\subsection{Knowledge Base}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
GET    /api/kb
       Query:   ?q=string (optional search)
       Returns: { entries: KBEntry[] }
       // Returns all approved entries, filtered by term search.

POST   /api/kb
       Body:    { term, definition, example? }
       Returns: { id, message: "Contribution submitted for review." }
       // Creates Contribution record. Not live until approved.

POST   /api/kb/[id]/flag
       Body:    { reason: string }
       Returns: { message: "Flag submitted." }
       // 3+ flags auto-downgrade entry (isApproved = false).
\end{lstlisting}
\end{tcolorbox}

\subsection{Ratings}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
POST   /api/ratings
       Body:    { songId: string, stars: number (1-5) }
       Returns: { id, message: "Rating saved." }
       // One per IP per song (upsert). Validates stars 1-5 and songId exists.
\end{lstlisting}
\end{tcolorbox}

\subsection{Worker (Cron)}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
GET    /api/worker
       Returns: { processed: number }
       // Vercel cron hits this every 60s. Processes up to 5 PENDING jobs.
       // Max 3 retries per job before FAILED.
\end{lstlisting}
\end{tcolorbox}

% ============================================================
\section{Folder Structure}
% ============================================================

\begin{tcolorbox}[codebox]
\begin{lstlisting}
app/
├── app/
│   ├── page.tsx                   # Landing + 3-tab input (home)
│   ├── layout.tsx                 # Root layout (Inter font, nav, footer, SEO)
│   ├── globals.css                # Tailwind + custom utilities
│   ├── song/[slug]/page.tsx       # 4-panel translation view
│   ├── library/page.tsx           # Public song library with search
│   ├── kb/page.tsx                # Slang KB browser + contribute modal
│   └── api/
│       ├── translate/route.ts     # POST — main translation pipeline
│       ├── audio/route.ts         # POST — Whisper transcription
│       ├── youtube/route.ts       # POST — yt-dlp + Whisper
│       ├── songs/
│       │   ├── route.ts           # GET — library with search + pagination
│       │   └── [slug]/route.ts    # GET — single song + translation
│       ├── kb/
│       │   ├── route.ts           # GET/POST — browse + contribute
│       │   └── [id]/flag/route.ts # POST — flag entry
│       ├── ratings/route.ts       # POST — star rating (1-5)
│       └── worker/route.ts        # GET — Vercel cron job processor
├── lib/
│   ├── ai.ts                      # All AI calls (Groq LLaMA + Whisper)
│   ├── ytdlp.ts                   # yt-dlp wrapper for YouTube audio
│   ├── prisma.ts                  # Prisma client singleton
│   └── utils.ts                   # slugs (nanoid), confidence formatting
├── prisma/
│   ├── schema.prisma              # 7 models, 4 enums
│   └── seed.ts                    # 209 KB term seed script
├── docs/
│   ├── architecture.md
│   ├── build-log.md
│   └── setup.md
├── docker-compose.yml             # Postgres 16 on port 5433
├── vercel.json                    # Cron: /api/worker every 60s
├── tailwind.config.js             # Custom ds-* colour tokens
├── .env.local                     # API keys (never committed)
└── package.json
\end{lstlisting}
\end{tcolorbox}

\begin{tcolorbox}[warnbox]
  \textbf{No components/ directory in v1.0.} All UI is inline in page files
  for speed of iteration. Component extraction is planned for v1.1 when the
  UI stabilises.
\end{tcolorbox}

% ============================================================
\section{AI Pipeline — Step by Step}
% ============================================================

\begin{tcolorbox}[enginebox, title={Full Pipeline (Audio Upload Path)}]
\begin{enumerate}
  \item \textbf{Receive file} → validate type and size → upload to temp storage
        → create Job record (\texttt{status: PENDING}).
  \item \textbf{Worker picks up job} → sets \texttt{status: PROCESSING}.
  \item \textbf{Transcription} → call Whisper transcription (via Groq
        Whisper endpoint — free, same API shape as OpenAI) → receive
        raw text → store on Job payload.
  \item \textbf{Show to user for edit} → frontend polls job, sees
        \texttt{status: AWAITING\_EDIT} → shows editable textarea.
        User confirms or edits → sends corrected lyrics back.
  \item \textbf{Preprocess} → split into lines → tag potential slang
        candidates via regex + known-term pattern matching.
  \item \textbf{KB Lookup} → query KBEntry table for all candidate terms →
        build context string of known definitions to pass to Groq.
  \item \textbf{Genre detection} → Groq (Llama 3.3 70B) classifies SDK vs non-SDK with
        confidence score:
        \begin{itemize}
          \item $>$0.85 non-SDK: return genre warning, offer override.
          \item $<$0.6 SDK confidence: proceed with disclaimer banner.
          \item $\geq$0.6 SDK: proceed normally.
        \end{itemize}
  \item \textbf{Groq LLaMA translation call} → structured JSON prompt (see
        Section~\ref{sec:prompt}) → Groq LLaMA 3.3 70B receives lyrics +
        KB context → returns all 4 panels + unknown terms.
  \item \textbf{Term extraction} → save unknown terms as KBCandidate records
        with Groq's provisional definitions.
  \item \textbf{Confidence scoring} → calculate per-term and overall score
        based on KB hit rate and Groq self-reported certainty.
  \item \textbf{Persist} → create Song + Translation records → return
        \texttt{\{slug\}} to frontend.
  \item \textbf{Frontend} → receives slug → redirects to
        \texttt{/song/[slug]} → renders all 4 panels.
\end{enumerate}
\end{tcolorbox}

\vspace{0.5em}

\textbf{Typed lyrics path} skips steps 1--4. Starts at step 5 directly.

\textbf{YouTube path} replaces step 3 with: always run yt-dlp to extract audio
(YouTube auto-captions are skipped because YouTube auto-translates Afrikaans to
broken English), then Groq Whisper transcription. If song already in library
by URL match, skip pipeline and serve cached result.

\subsection{Job Worker Design}

The job queue is a Postgres table (the \texttt{Job} model). The worker is a
Next.js API route that gets triggered on a schedule:

\begin{tcolorbox}[codebox]
\begin{lstlisting}
// lib/jobs/worker.ts
// Called by: GET /api/worker (hit by a Vercel cron job every 30s)
// 1. Query: SELECT * FROM Job WHERE status = PENDING ORDER BY createdAt LIMIT 5
// 2. For each job: set status = PROCESSING, run pipeline, set COMPLETE or FAILED
// 3. On failure: increment attempts. After 3 attempts: set status = FAILED.
\end{lstlisting}
\end{tcolorbox}

\begin{tcolorbox}[warnbox]
  \textbf{Vercel cron} (free tier) supports cron jobs with a minimum interval
  of 60 seconds on the free plan. For v1.0 this is fine. If we need faster
  processing, we switch to a persistent worker on Railway later.
\end{tcolorbox}

\subsection{Groq LLaMA Translation Prompt}
\label{sec:prompt}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
SYSTEM:
You are DecodedSound — a cultural translation engine specialised in SDK
(esdeekid) music from the Cape Flats, South Africa. You have deep knowledge
of the dialect, phonetic wordplay, Afrikaans and Xhosa borrowings, and the
cultural references of this genre.

You will receive:
- Raw song lyrics
- A KB context block of known terms and definitions

Produce a single JSON object with exactly these keys:
{
  "plainTranslation": string,       // full song in plain English, natural prose
  "lineByLine": [                   // one object per lyric line
    {
      "original": string,
      "translation": string,
      "flaggedTerms": string[]      // terms from this line that are in KB or unknown
    }
  ],
  "culturalContext": string,        // 2-4 paragraph narrative, accessible prose
  "unknownTerms": [                 // terms NOT in KB
    {
      "term": string,
      "provisionalDefinition": string,
      "confidence": number          // 0.0 - 1.0
    }
  ],
  "genreConfidence": number,        // 0.0 - 1.0 SDK genre match
  "overallConfidence": number       // 0.0 - 1.0 translation confidence
}

Rules:
- Never hallucinate definitions. If a term is unknown, include it in
  unknownTerms with your best guess and a low confidence score.
- Flag uncertainty. Never present a guess as a fact.
- Output strict JSON only. No markdown, no preamble, no explanation.
- Cultural context must be readable by someone with zero knowledge of SDK.
- Plain translation must read naturally — not word-for-word literal.
\end{lstlisting}
\end{tcolorbox}

% ============================================================
\section{AI Provider Strategy}
% ============================================================

DecodedSound uses a \textbf{single-provider, zero-cost AI stack} for v1.0.
All AI calls go through Groq via the OpenAI-compatible SDK --- swapping
providers means changing two lines of code, nothing else.

\begin{tcolorbox}[prdbox, title={Groq --- Single Provider for All AI Tasks}]
\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{3.5cm} L{3cm} L{3cm} L{3.5cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Task}} &
  \textcolor{white}{\textbf{Provider}} &
  \textcolor{white}{\textbf{Model}} &
  \textcolor{white}{\textbf{Free Limit}} \\
  \rowcolor{rowalt}
  Translation, line-by-line, cultural context &
  Groq & llama-3.3-70b-versatile &
  14,400 req/day \\
  Genre detection &
  Groq & llama-3.3-70b-versatile &
  (shared limit) \\
  \rowcolor{rowalt}
  KB term extraction &
  Groq & llama-3.3-70b-versatile &
  (shared limit) \\
  Audio transcription &
  Groq Whisper & whisper-large-v3 &
  7,200 audio-sec/hr \\
\end{tabular}
\end{center}
\end{tcolorbox}

\subsection{Why Groq Only}

\begin{itemize}
  \item \textbf{Speed} --- Groq's inference is the fastest available (500+ tok/s).
        Translation feels near-instant to the user.
  \item \textbf{Free tier is the most generous} --- 14,400 req/day covers all
        translation + detection + KB extraction needs for early traction.
  \item \textbf{Single API key} --- one provider means one key, one bill, one
        rate-limit to monitor. Simpler to operate as a 2-person team.
  \item \textbf{Whisper included} --- Groq offers a free Whisper endpoint,
        so transcription costs nothing and uses the same SDK.
  \item \textbf{Easy to swap later} --- all calls go through the OpenAI SDK.
        If quality or limits become an issue, we can switch to Gemini, Claude,
        or OpenRouter by changing \texttt{baseURL} and \texttt{apiKey} only.
\end{itemize}

\subsection{Provider Abstraction Layer}

All AI calls go through a single file: \texttt{lib/ai.ts}.
Swapping providers never touches business logic:

\begin{tcolorbox}[codebox]
\begin{lstlisting}
// lib/ai.ts
import OpenAI from 'openai'

const groq = new OpenAI({
  baseURL: 'https://api.groq.com/openai/v1',
  apiKey: process.env.GROQ_API_KEY,
})

// Translation -> groq.chat.completions.create({ model: 'llama-3.3-70b-versatile', ... })
// Genre detect -> groq.chat.completions.create({ model: 'llama-3.3-70b-versatile', ... })
// Transcribe  -> groq.audio.transcriptions.create({ model: 'whisper-large-v3', ... })
\end{lstlisting}
\end{tcolorbox}

\subsection{When We'd Pay}

We stay fully free until one of these triggers:
\begin{itemize}
  \item Groq free limits (14,400 req/day) consistently maxed out ---
        Groq paid tier is still very cheap.
  \item Quality ceiling hit --- if LLaMA 3.3 70B's translation quality
        is insufficient for complex SDK wordplay, we evaluate Gemini 2.5 Flash
        or Claude 3.5 Sonnet as a premium upgrade.
  \item At meaningful scale, we evaluate whether a dedicated provider
        gives better quality ROI than the current setup.
\end{itemize}

% ============================================================
\section{Tech Stack — Final Decisions}
% ============================================================

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{3.5cm} L{4cm} L{6cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Layer}} &
  \textcolor{white}{\textbf{Technology}} &
  \textcolor{white}{\textbf{Why}} \\
  \rowcolor{rowalt}
  Framework & Next.js 14 (App Router) &
  Fullstack in one repo — frontend + API routes. No separate backend. \\
  Language & TypeScript &
  Type safety across DB, API, and UI. Catches bugs before runtime. \\
  \rowcolor{rowalt}
  Database & Postgres (local dev) $\to$ Supabase (production) &
  Local is free and fast. Supabase free tier when we go live — also handles file storage, killing S3. \\
  ORM & Prisma &
  Type-safe queries, migrations built in, plays perfectly with TypeScript and Supabase. \\
  \rowcolor{rowalt}
  Transcription & Groq Whisper (whisper-large-v3) &
  Best multilingual transcription. Free tier. Same SDK as translation. \\
  Translation AI & Groq LLaMA 3.3 70B &
  Fast inference, generous free tier (14,400 req/day). Strong cultural reasoning. \\
  \rowcolor{rowalt}
  YouTube Extraction & yt-dlp (CLI, called from API route) &
  Industry standard for YouTube audio. Free. \\
  Styling & Tailwind CSS &
  Fast, responsive, no CSS files to manage. \\
  \rowcolor{rowalt}
  Deployment & Vercel (free tier) &
  Zero config. Deploys on every push. Free cron jobs for the job worker. \\
  Job Queue & Postgres Job table + Vercel cron &
  No extra service. We control it. Scales fine for v1.0. \\
  \rowcolor{rowalt}
  File Storage & Supabase Storage (when live) &
  Replaces S3 entirely. Same free tier account as the DB. \\
  Auth & Not in v1.0 &
  Clerk is ready to add in v1.5 when accounts are needed. \\
\end{tabular}
\end{center}

\begin{tcolorbox}[accentbox]
  \textbf{What we removed from v1:} AWS Lambda, AWS SQS, AWS S3, AWS RDS,
  FastAPI, separate Python backend. All replaced by Next.js API routes +
  Postgres + Supabase Storage. Same capability, a fraction of the complexity.
\end{tcolorbox}

% ============================================================
\section{Environment Variables}
% ============================================================

\begin{tcolorbox}[codebox]
\begin{lstlisting}
# .env.local (never commit this file)

# Database (local Docker: port 5433, see docker-compose.yml)
DATABASE_URL="postgresql://decodedsound:decodedsound@localhost:5433/decodedsound"

# AI — Groq handles ALL AI tasks (translation, detection, transcription)
GROQ_API_KEY=""            # Groq — LLaMA 3.3 70B + Whisper

# Supabase (add when going live, leave blank in local dev)
NEXT_PUBLIC_SUPABASE_URL=""
NEXT_PUBLIC_SUPABASE_ANON_KEY=""
SUPABASE_SERVICE_ROLE_KEY=""

# App
NEXT_PUBLIC_APP_URL="http://localhost:3000"
WORKER_SECRET=""           # secret to protect /api/worker cron endpoint
\end{lstlisting}
\end{tcolorbox}

% ============================================================
\section{Milestone Plan}
% ============================================================

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{C{1.3cm} L{3.5cm} L{8.7cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Week}} &
  \textcolor{white}{\textbf{Milestone}} &
  \textcolor{white}{\textbf{Deliverables}} \\
  1--2 & \textcolor{successgreen}{Foundation} &
  Repo, Prisma schema + local DB, Next.js shell, Tailwind setup,
  \texttt{.env.local}, Groq Whisper test call, Groq LLaMA test call.
  \textcolor{successgreen}{\textbf{DONE}} \\
  3--4 & \textcolor{successgreen}{Core Pipeline} &
  Typed lyrics $\to$ Groq LLaMA $\to$ 4-panel output working end-to-end.
  Job table + worker. KB seeded with 209 terms.
  \textcolor{successgreen}{\textbf{DONE}} \\
  5--6 & \textcolor{successgreen}{Audio \& YouTube} &
  Audio upload with Whisper + edit step. YouTube link with
  yt-dlp audio extraction (captions skipped). Caching for known songs.
  \textcolor{successgreen}{\textbf{DONE}} \\
  7--8 & KB \& Community &
  KB lookup in pipeline. Confidence scoring. Flag form. Contribute
  form. Admin moderation queue (basic internal page). \\
  \rowcolor{rowalt}
  9--10 & Library \& Sharing &
  Public song library. Search by artist. Star ratings. Shareable
  URLs. Genre detection + mismatch warning. \\
  11--12 & Polish \& Errors &
  All error states. Mobile-responsive UI. Full error logging.
  Performance pass. Accessibility basics. \\
  \rowcolor{rowalt}
  13--14 & Beta \& Launch &
  Internal beta. KB at 500+ terms. Bug fixes. Vercel deploy.
  Public launch. \\
\end{tabular}
\end{center}

% ============================================================
\section{MVP Scope}
% ============================================================

\subsection*{In v1.0}
\begin{itemize}
  \item Typed lyrics, audio upload, YouTube link input
  \item 4-panel output: plain translation, line-by-line, slang dictionary,
        cultural context
  \item Genre detection with SDK-only scope and friendly warnings
  \item Slang KB: 500+ AI-seeded terms, flag + contribute forms
  \item Admin moderation queue (internal, not public-facing)
  \item Public song library with search and ratings
  \item Shareable URLs per song
  \item Fully open — no account required for anything
  \item Web only, English UI
\end{itemize}

\subsection*{Explicitly NOT in v1.0}
\begin{itemize}
  \item User accounts or authentication
  \item Mobile application
  \item Any genre other than SDK / esdeekid
  \item Non-English UI
  \item SoundCloud or Spotify audio extraction
  \item PDF / image export
  \item Embeddable widget or public API
  \item Monetization of any kind
  \item Artist dashboard or analytics
  \item English $\to$ SDK reverse translation (Phase 2)
\end{itemize}

\subsection*{Phase 2 — v1.5 (Weeks 14--24)}
\begin{itemize}
  \item \textbf{English $\to$ SDK Reverse Translation} — user types plain
        English and gets SDK-style output back. Fun, viral, drives engagement.
        Powered by the same KB in reverse. See Section~\ref{sec:reverse} for
        full feature spec.
  \item SoundCloud and Spotify integration
  \item User accounts (optional — for saved history)
  \item Community KB voting and contributor leaderboard
  \item Artist song-claim and official commentary
  \item PDF / image export of translated lyrics
  \item Access limits if needed (daily cap for guests)
  \item Analytics dashboard (internal)
  \item Monetization decision and implementation begins
\end{itemize}

\subsection*{Phase 3 — v2.0 (Month 6+)}
\begin{itemize}
  \item Mobile application (React Native)
  \item Genre expansion: Amapiano, Gqom, Kwaito (separate KB per genre)
  \item Multilingual UI: Afrikaans, Zulu, French
  \item Embeddable widget for external sites
  \item Public API (B2B licensing)
  \item Real-time lyric translation
\end{itemize}

% ============================================================
\section{Feature Spec: English $\to$ SDK Reverse Translation}
\label{sec:reverse}
% ============================================================

\begin{tcolorbox}[accentbox]
  \textbf{Inspired by:} esdictionary.com (The Right Note, YouTube). Their
  tool is a static lookup table — ours uses the live KB + AI to generate
  contextually authentic SDK-style output, not just word swaps.
\end{tcolorbox}

\vspace{0.6em}

The reverse translation mode lets users type plain English and receive
SDK-style output — the same language, slang, and phonetic style that
EsDeeKid uses. This is the feature that makes DecodedSound \textit{fun}
and shareable, not just educational.

\subsection{User Stories — Reverse Mode}

\begin{tcolorbox}[storybox, title={US-17 — Translate English to SDK Style}]
  \textbf{As a} fan, \textbf{I want to} type something in plain English and
  get it back in SDK style, \textbf{so that} I can engage with the culture
  and share it with friends.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item A toggle on the input switches between ``SDK $\to$ English'' and
          ``English $\to$ SDK'' modes. Default is SDK $\to$ English.
    \item In reverse mode, user types plain English text (up to 500 words).
    \item Output is a single panel: the SDK-style rewrite.
    \item Output uses real KB terms where appropriate — not invented slang.
    \item AI is instructed to match EsDeeKid's phonetic style, cadence,
          and vocabulary as closely as possible.
    \item A disclaimer is shown: ``AI-generated SDK style — not verified
          by native speakers.''
  \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[storybox, title={US-18 — Share a Reverse Translation}]
  \textbf{As a} user, \textbf{I want to} share my SDK-style output,
  \textbf{so that} I can post it or send it to friends.\\[0.4em]
  \textbf{Done when:}
  \begin{itemize}
    \item Reverse translations get a shareable URL like forward translations.
    \item A ``Copy text'' button copies just the SDK output for pasting
          into messages or social media.
    \item Output is clearly labelled as AI-generated SDK style.
  \end{itemize}
\end{tcolorbox}

\subsection{How It Works — Reverse Pipeline}

\begin{tcolorbox}[prdbox, title={Reverse Translation Pipeline}]
\begin{enumerate}
  \item User types plain English text and selects ``English $\to$ SDK'' mode.
  \item System queries KB for high-confidence SDK terms relevant to the
        input's semantic content.
  \item Groq LLaMA receives: plain English input + KB context of real SDK terms
        + system prompt instructing it to rewrite in authentic EsDeeKid style.
  \item Output is a single SDK-style rewrite using real KB vocabulary
        where possible, AI-inferred style where not.
  \item Result stored with \texttt{sourceType: REVERSE\_TRANSLATION} in DB.
  \item Shareable URL generated. Disclaimer banner shown.
\end{enumerate}
\end{tcolorbox}

\subsection{Groq LLaMA Prompt — Reverse Mode}

\begin{tcolorbox}[codebox]
\begin{lstlisting}
SYSTEM:
You are DecodedSound in reverse mode. Your job is to rewrite plain English
text in the style of EsDeeKid (SDK) — a Cape Flats hip-hop artist from
South Africa.

EsDeeKid's style includes:
- Cape Flats slang and dialect
- Afrikaans words and phonetic borrowings
- Short, punchy sentences with street cadence
- Phonetic wordplay and double meanings
- The following verified KB terms (use these where natural): {kb_terms}

Rules:
- Only use KB terms where they fit naturally. Do not force them.
- Do not invent slang that isn't in the KB — use AI judgement for style,
  not vocabulary.
- Keep the core meaning of the input intact.
- Output the SDK rewrite only. No explanation, no preamble.
\end{lstlisting}
\end{tcolorbox}

\subsection{DB Change for Reverse Mode}

One addition to the \texttt{SourceType} enum:

\begin{tcolorbox}[codebox]
\begin{lstlisting}
enum SourceType {
  TYPED_LYRICS
  AUDIO_UPLOAD
  YOUTUBE_LINK
  REVERSE_TRANSLATION   // new in v1.5
}
\end{lstlisting}
\end{tcolorbox}

\subsection{Competitive Advantage Over esdictionary.com}

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{4.5cm} L{4cm} L{5cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Feature}} &
  \textcolor{white}{\textbf{esdictionary.com}} &
  \textcolor{white}{\textbf{DecodedSound}} \\
  \rowcolor{rowalt}
  Translation method & Static word lookup & AI + live KB context \\
  Handles sentences & No — word by word & Yes — full sentence rewrite \\
  \rowcolor{rowalt}
  KB grows over time & No — frozen & Yes — every submission adds terms \\
  Phonetic style matching & No & Yes — Groq LLaMA mimics cadence \\
  \rowcolor{rowalt}
  Forward translation & Yes & Yes (core feature) \\
  Cultural context & No & Yes \\
  \rowcolor{rowalt}
  Audio / YouTube input & No & Yes \\
\end{tabular}
\end{center}

% ============================================================
\section{Success Metrics}
% ============================================================

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{4.5cm} L{3cm} L{6cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Metric}} &
  \textcolor{white}{\textbf{Target}} &
  \textcolor{white}{\textbf{How Measured}} \\
  \rowcolor{rowalt}
  Translation accuracy (user-rated) & $\geq$85\% good &
  Post-translation star rating \\
  Monthly active users & 5,000 by month 3 &
  Vercel analytics \\
  \rowcolor{rowalt}
  Unique songs translated & 1,000 in library &
  DB count \\
  Avg session duration & $>$4 minutes &
  Analytics \\
  \rowcolor{rowalt}
  KB terms at launch & 500+ &
  DB count \\
  KB terms at 6 months & 2,000+ &
  DB count \\
  \rowcolor{rowalt}
  Community contributions/month & 100+ by month 3 &
  Submission logs \\
  Shares/month & 500+ by month 2 &
  URL click tracking \\
\end{tabular}
\end{center}

% ============================================================
\section{Risks \& Mitigations}
% ============================================================

\renewcommand{\arraystretch}{1.5}
\begin{center}
\begin{tabular}{L{4cm} L{2.5cm} L{7cm}}
  \rowcolor{brandpurple!80}
  \textcolor{white}{\textbf{Risk}} &
  \textcolor{white}{\textbf{Likelihood}} &
  \textcolor{white}{\textbf{Mitigation}} \\
  \rowcolor{rowalt}
  Whisper inaccuracy on fast delivery & High &
  User edit step before translation. Post-launch fine-tuning. \\
  Slang evolves faster than KB & High &
  AI extracts candidates from every submission. Community validates. \\
  \rowcolor{rowalt}
  Cultural misrepresentation & Medium &
  Confidence scoring. Flagging. ``AI-generated'' label on all outputs. \\
  Groq LLaMA hallucination & Medium &
  Explicit prompt instruction: flag unknown, never guess as fact. \\
  \rowcolor{rowalt}
  Copyright on YouTube extraction & Medium &
  Audio used only for transcription, never stored or served. Fair-use argument. \\
  Low community volume early & Medium &
  AI-first KB means launch doesn't depend on community. \\
  \rowcolor{rowalt}
  Abuse of open flag/contribute & Low--Med &
  IP rate limiting. Honeypot fields. Moderation queue. \\
  Scope creep to other genres & Low &
  Hard line in this document. SDK only until v1.0 ships. \\
\end{tabular}
\end{center}

% ============================================================
\section{Open Questions}
% ============================================================

\begin{enumerate}
  \item \textbf{Monetization} — Must be decided before v1.5 architecture.
        Options: freemium (guest cap, paid unlimited), B2B API, ads.
        Current architecture does not block any of these.
  \item \textbf{Artist rights / DMCA} — Do artists have the right to remove
        their song from the public library? We need a policy before launch.
  \item \textbf{Content moderation policy} — Explicit content and illegal
        references will appear in SDK music. What is the library policy?
        Recommended: no filter in v1.0, community flagging handles it.
  \item \textbf{Launch partnerships} — SoundCloud, Audiomack, or SA music
        blogs as launch partners for initial KB seeding and user acquisition.
\end{enumerate}

% ============================================================
%  CLOSE
% ============================================================
\vspace{2em}
\begin{tcolorbox}[darkbox]
  \centering
  \textcolor{white}{\Large\bfseries DecodedSound}\\[0.5em]
  \textcolor{brandlight}{Making the culture accessible to the world.}\\[0.8em]
  \textcolor{midgray}{\small
    Full PRD + Engineering Spec v3.3\quad|\quad March 2026\quad|\quad
    SDK only (v1.0)\quad|\quad Confidential
  }
\end{tcolorbox}

\end{document}